%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,a4paper,sans]{moderncv}       

% moderncv themes
\moderncvstyle{perso}                            
\moderncvcolor{darkblue}                         
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
\usepackage[english]{babel}
\usepackage[T1]{fontenc}

% adjust the page margins
\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}

\setlength{\hintscolumnwidth}{3.2cm}                % if you want to change the width of the column with the dates
\setlength{\beforesectionvspace}{3ex}               % space above section title
\setlength{\beforesubsectionvspace}{2ex}            % space above subsection title

\renewcommand\colorhref[3][black]{\href{#2}{\textit{\small\color{#1}#3}}}

%%%%%%%%%%%%%%%%%%%%% publi and conf with biblatex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{csquotes}
\usepackage[backend=biber,
bibstyle=ieee,
citestyle=numeric,
sorting=ydmdddnt, 
date=year,
isbn=false,
url=true,
doi=false,
dashed=false,
maxnames=100]{biblatex}

\BiblatexSplitbibDefernumbersWarningOff
\AtEveryBibitem{%
    \clearfield{number}
}

\usepackage[normalem]{ulem} %for \uline

\usepackage{xstring}
\usepackage{etoolbox}
\newboolean{bold}


\DeclareSourcemap{
    \maps[datatype=bibtex]{
        \map{
            \step[fieldsource=dates]
            \step[fieldset=usera,origfieldval]
        }
    }
}


\DeclareSourcemap{
    \maps[datatype=bibtex]{
        \map{
            \step[fieldsource=video]
            \step[fieldset=userb,origfieldval]
        }
    }
}

\newcommand{\underlineauthor}[1]{%
    \DeclareNameFormat{author}{%
        \setboolean{bold}{false}%
        \renewcommand{\do}[1]{\expandafter\ifstrequal\expandafter{\namepartfamily}{####1}{\setboolean{bold}{true}}{}}%
        \docsvlist{#1}%
        \ifthenelse{\value{listcount}=1}
        {%
            {\expandafter\ifthenelse{\boolean{bold}}{\uline{\namepartgiveni\addspace\namepartfamily }}{\namepartgiveni\addspace\namepartfamily}}%
        }{\ifnumless{\value{listcount}}{\value{liststop}}
            {\expandafter\ifthenelse{\boolean{bold}}{\addcomma\addspace \uline{\namepartgiveni\addspace\namepartfamily }}{\addcomma\addspace \namepartgiveni\addspace\namepartfamily }}%
            {\expandafter\ifthenelse{\boolean{bold}}{\addcomma\addspace \uline{\namepartgiveni\addspace \namepartfamily \addcomma\isdot}}{\addcomma\addspace \namepartgiveni\addspace\namepartfamily\addcomma \addcomma\isdot}}%
        }
        \ifthenelse{\value{listcount}<\value{liststop}}
        {\addcomma\space}{}
    }
}
\ExecuteBibliographyOptions{doi=false}
\newbibmacro{string+doi}[1]{%
    \iffieldundef{doi}{#1}{\href{http://dx.doi.org/\thefield{doi}}{#1}}
}
\newbibmacro{string+url}[1]{%
    \iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}
}

\newbibmacro{url+video}{%
    \iffieldundef{userb}{\iffieldundef{url}{}{Website: \url{\thefield{url}}}}{Video: \url{\thefield{userb}}}
}

\newbibmacro{dates}{%
    \iffieldundef{usera}{}{, \thefield{usera}}
}


\DeclareFieldFormat{title}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
\DeclareFieldFormat{journaltitle}{\usebibmacro{string+doi}{\mkbibemph{#1}}}
\DeclareFieldFormat[inproceedings]{booktitle}{\usebibmacro{string+url}{\mkbibemph{#1}}}
\DeclareFieldFormat[inproceedings]{url}{\usebibmacro{url+video}}
%\DeclareListFormat[inproceedings]{location}{%
%        \usebibmacro{list:delim}{#1}%
%        #1\isdot
%        \usebibmacro{list:andothers}
%}

\underlineauthor{Monsel, Juliette}

\renewbibmacro*{date}{\ifentrytype{inproceedings}{\iffieldundef{usera}{}{, \thefield{usera}}}{}
}
%\renewbibmacro*{author/translator+others}{}
\DeclareFieldFormat[article]{pages}{\usebibmacro{string+doi}{#1}}
\DeclareFieldFormat[article]{volume}{\usebibmacro{string+doi}{\textbf{#1}}}
%\renewbibmacro*{date+extrayear}{}
\renewbibmacro*{issue+date}{}

%
\newcommand*{\bibyear}{}
\renewbibmacro{in:}{}
\setlength{\bibitemsep}{0.2em}
\defbibenvironment{bibliography}
{\list
    {\iffieldequals{year}{\bibyear}
        {}
        {\printfield{year}%
            \savefield{year}{\bibyear}}}
    {\setlength{\topsep}{0pt}% layout parameters based on moderncvstyleclassic.sty
        \setlength{\labelwidth}{\hintscolumnwidth}%
        \setlength{\labelsep}{\separatorcolumnwidth}%
        \setlength{\itemsep}{\bibitemsep}%
        \leftmargin\labelwidth%
        \advance\leftmargin\labelsep}%
    \sloppy\clubpenalty4000\widowpenalty4000}
{\endlist}
{\item}

%\DeclareFieldFormat{usera}{\textbf{#1}}

%\AtEveryBibitem{%
%    \csappto{blx@bbx@\thefield{entrytype}}{% put at end of entry
%        \iffieldundef{usera}{}{%
%            \space\printfield{usera}
%        }
%    }
%}

\addbibresource{../publications.bib}
\addbibresource{../conf.bib}
\defbibheading{bibliography}[\refname]{}



\DeclareSortingTemplate{ydmdddnt}{
    \sort{
        \field{presort}
    }
    \sort[final]{
        \field{sortkey}
    }
    \sort[direction=descending]{
        \field{year}
    }
    \sort[direction=descending]{
        \field[padside=left,padwidth=2,padchar=0]{month}
        \literal{99}
    }
    \sort[direction=descending]{
        \field{day}
    }
    \sort{
        \field{journaltitle}
    }
    \sort{
        \field{author}
        \field{editor}
    }
    \sort{
        \field{title}
    }
} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% add icons for resaerch social media
\usepackage{fontawesome5}
\renewcommand*\orcidsocialsymbol{{\faIcon{orcid}}~} % <=========================
%\newcommand*\researcheridsocialsymbol{{\faIcon{parking}}~} % <========= \aiGoogleScholarSquare
%\newcommand*\researchgatesocialsymbol{{\aiResearchGate}~}   % <========= \aiResearchGateSquare

% personal data
\name{Juliette}{Monsel}
\title{Researcher in theoretical physics}                               % optional, remove / comment the line if not wanted
\address{Gothenburg, Sweden}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
%\phone[mobile]{}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{monsel@chalmers.se}                               % optional, remove / comment the line if not wanted
%\email{juliette.monsel@gmx.fr}                               % optional, remove / comment the line if not wanted
\homepage{j4321.github.io/juliette.monsel}                         % optional, remove / comment the line if not wanted
%\social[linkedin]{www.linkedin.com/in/juliette-monsel}                        % optional, remove / comment the line if not wanted
\social[orcid]{0000-0002-4965-6794}                        % optional, remove / comment the line if not wanted
%~\social[researcherid]{AAH-5591-2020} 
%\social[twitter]{jdoe}                             % optional, remove / comment the line if not wanted
%\social[github]{j4321}                             % optional, remove / comment the line if not wanted
\extrainfo{Nationality: French}                     % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{\vskip-5mm Research interests: stochastic thermodynamics, quantum open systems, quantum optics, optomechanics and electronic transport.}                                 



%-----       resume       ---------------------------------------------------------
\begin{document}
\renewcommand{\labelitemi}{$\bullet$}

\makecvtitle

\vspace{-0.55cm}
\section{Education}
\cventry[0.5em]{2020}{Qualification}{National Council of Universities (CNU)}{France}{}{Certificate allowing me to apply to ``Maître de Conférence'' positions, permanent Assistant Professor positions with an important teaching component, at French universities.}

\cventry[0.3em]{2019}{Ph.D.}{Université Grenoble Alpes}{France}{}{Theoretical Physics.}
    
\cventry[0.3em]{2016}{M.Sc.}{École Normale Supérieure de Lyon}{France}{}{Major: Physics, Mention: highest honors}  
\cventry[0.3em]{2014}{B.Sc.}{École Normale Supérieure de Lyon}{France}{}{Major: Physics, Mention: highest honors}
\cventry[0.3em]{2011 -- 2013}{Classe Préparatoire}{Lycée La Martinière Monplaisir}{Lyon, France}{}{Two-year intensive course preparing for the competitive entrance examinations to French leading institutions of higher education. Track: Mathematics-Physics.}
%\cventry{July 2011}{Baccalauréat -- High school diploma}{Lycée du Val de Saône}{Trévoux, France}{}{Scientific course, Mention: highest honors, GPA: 18.2/20 -- A$^+$}

\section{Research experience}
%TODO: detail projects
\cventry[0.5em]{2020 -- current}{Postdoctoral researcher}{Department of Microtechnology and Nanoscience, Chalmers University of Technology}{Gothenburg, Sweden}{}{
    Advisor: Janine Splettstoesser. Quantum thermodynamics.
    \begin{itemize}
        \item Studied thermodynamic of electronic transport
        \item Analyzed optomechanical cooling in a thermodynamic perspective
    \end{itemize}
} 
\cventry[0.5em]{2019 -- 2020\\(4 months)}{Postdoctoral researcher}{Institut Néel}{Grenoble, France}{}{Advisor: Alexia Auffèves. Quantum thermodynamics and optomechanics.
\begin{itemize}
    \item Explored the potential of carbon nanotubes for thermodynamic experiments
    \item Studied stochastic thermodynamics with Kerr resonators
\end{itemize}} 
\cventry[0.5em]{2016 -- 2019\\(3 years, 2 months)}{Doctoral researcher}{Institut Néel}{Grenoble, France}{}
{
    Supervisor: Alexia Auffèves. Quantum thermodynamics and optomechanics.
    \begin{itemize}
        \item Demonstrated the potential of hybrid optomechanical systems and one-dimensional atoms to experimentally explore quantum thermodynamics
        \item Proposed methods to define and measure work in the quantum regime
    \end{itemize}
} 
\cventry[0.5em]{2016\\(4 months)}{Master intern}{Institut Néel}{Grenoble, France}{}{Supervisor: Alexia Auffèves. Fluctuation theorems in a hybrid optomechanical system.%
%\begin{itemize}%
%\item Simulated trajectories of the hybrid optomechanical system using a quantum jump approach
%\item Computed the irreversibility for a single trajectory and checked Jarzynski's equality
%\end{itemize}
}
\cventry[0.5em]{2015\\(3 months)}{Master intern}{Institut Néel}{Grenoble, France}{}{Supervisor: Alexia Auffèves. Hybrid optomechanical system in the ultra-strong coupling regime.%
%\begin{itemize}%
%    \item Simulated trajectories of the hybrid optomechanical system using Python programming language
%    \item Showed that the system can behave like a ``mechanical laser'' or a cooling system
%\end{itemize} 
}
%%\cventry{2014\\(6 Fridays)}{Experimental Project}{Laboratoire de Physique}{ENS de Lyon}{supervisor: Antoine Naert}{Energy exchanges with a dissipative thermostat.
%\begin{itemize}
%\item Studied the energy exchanges between a rarefacted granular gas and a blade
%\end{itemize}
%}
\cventry[0.5em]{2014\\(2 months)}{Bachelor intern}{Institut Lumière Matière}{Lyon, France}{}{Supervisor: Julien Laverdant. Experimental control of polarization with a spatial light modulator.%
%%\begin{itemize}%
%%\item Simulated the focusing of a laser beam with Matlab
%%\item Successfully generated a radially polarized beam with the spatial light modulator
%%\end{itemize}
}

\section{Teaching experience}
\cventry{2017, 2018\\(64 hours/year)}{Teaching Assistant}{Université Grenoble Alpes}{France}{}{Newtonian mechanics for first year undergraduates.
\begin{itemize}
    \item Supervised students during tutorials (2$\times$1,5 hours/week, $\sim$ 30 students) and practical work (3 hours/week, $\sim$ 15 students)
    \item Graded examinations and practical work reports
    \item Wrote exercises for the examinations
\end{itemize}
}

\cventry{2013 -- 2014\\(7 months)}{Tutor for homework assistance}{Trait d'Union program}{Villeurbanne, France}{}{Took part in a homework assistance program for students from high schools in disadvantaged areas (2 hours/week).
    %    \begin{itemize}
    %        \item Supervised high school students while they were doing their homework (two hours a week)
    %        \item Met people from varied social and cultural background
    %    \end{itemize}
}
\subsection{Student supervision}
\cvitem[0.5em]{Apr. -- Jul. 2022}{Co-supervisor of a master student from École Normale Supérieure de Lyon (France) at MC2, Chalmers University of Technology for a four-month project.}
\cvitem[0.5em]{Oct. 2021 -- Jul. 2022}{Co-supervisor of a master student from University of Regensburg (Germany) at MC2, Chalmers University of Technology.}
\cvitem[0.5em]{2020 -- current}{Official assistant supervisor of a Ph.D. student at MC2, Chalmers University of Technology.}
\cvitem[0.5em]{2016}{Informal co-supervisor of a first-year master student during his two-month internship at the Institut Néel, Grenoble, France.}

\subsection{Training}
\cventry[0.5em]{2017}{How to develop as a teacher}{Doctoral school of Physics}{Grenoble, France}{}{Two-day training program on communication and group animation techniques for teaching.}
\cventry[0.5em]{2016 -- 2019}{Research and Higher Education (RES) label}{Doctoral school of Physics}{Grenoble, France}{}{Teaching oriented Ph.D. program leading to the production of a portfolio documenting the development of my teaching and research skills (in French): \url{http://juliette-monsel.byethost15.com}.}
\cventry[0.5em]{2016}{Introduction to the profession of teacher-researcher}{Doctoral school of Physics}{Autrans, France}{}{Three-day workshop on topics related to teaching at the university.}

\section{Awards and Grants}
\cvitem{Submitted}{\textbf{EIC Pathfinder Challenge}: \colorhref{https://eic.ec.europa.eu/eic-funding-opportunities/calls-proposals/eic-pathfinder-challenge-alternative-approaches-quantum-information-processing-communication-and_en}{Alternative approaches to Quantum Information
        Processing, Communication, and Sensing}, as part of a European consortium (Austria, Germany, Czech Republic and Sweden). I took part in the proposal writing and the budget elaboration.}
\cvitem{2022}{\textbf{Travel grant} from Chalmers Foundation (\colorhref{https://www.chalmers.se/en/foundation/scholarshipsandgrants/Pages/CFFeng.aspx}{Chalmersska forskningsfonden}) to go to Vienna for a research visit and the annual Quantum Thermodynamics Conference in July 2023.}
\cvitem{2020}{\textbf{Spinger Thesis Award}, recognizing outstanding Ph.D. research.}
\cvitem{2016}{\textbf{Ph.D. grant} from the \colorhref{http://www.fondation-cfm.fr/}{CFM Foundation for Research}.}


\nocite{*}
\section{Publications}
\subsection{Preprints}
\printbibliography[title={Preprints}, keyword={preprint}]
\renewcommand*{\bibyear}{}
\subsection{Articles}
\printbibliography[title={Articles}, keyword={publi}]
\renewcommand*{\bibyear}{}
\subsection{Books}
\printbibliography[title={Books}, keyword={book}]
\renewcommand*{\bibyear}{}


\section{Conferences and seminars} 
\subsection{Invited talks}
\printbibliography[title={Invited talks}, keyword={invited}]
\renewcommand*{\bibyear}{}
%\vspace{0.1cm}
\subsection{Contributed talks}
\printbibliography[title={Contributed talks}, keyword={contributed}]
\renewcommand*{\bibyear}{}
%\vspace{0.1cm}
\subsection{Invited seminars}
\printbibliography[title={Invited seminars}, keyword={seminar}]
\renewcommand*{\bibyear}{}
%\vspace{0.1cm}
\subsection{Contributed posters}
\printbibliography[title={Contributed posters}, keyword={poster}]
\renewcommand*{\bibyear}{}


\section{Service to the community}
\cvitem[0.5em]{Reviewer}{Sci. Rep. (2022), Phys. Rev. A (2021, 2022), J. Stat. Mech. Theory Exp. (2021), Phys. Rev. E (2021, 2022), J. Phys. A Math. (2021), New J. Phys. (2020), Commun. Phys. (2020)}
\cvitem[0.5em]{Scientific outreach}{Speaker and guide (2016 -- 2019) at the ``Fête de la Science'', a yearly national French event during which scientific institutions promote science through animations and laboratory tours aimed at high school students and the general public.}


%~\newpage
\section{Volunteer experience}
\cventry[0.5em]{2020 -- current}{Cykelköket}{}{Gothenburg, Sweden}{}{The ``Bike kitchen'' is an open Do-It-Yourself bicycle workshop.
    \begin{itemize}
        \item Helped people repair their bikes
        \item Took part in the administration of the workshop as a board member from Sep. 2020 to Sep. 2022.
    \end{itemize}
}
\cventry[0.5em]{2017 -- 2020}{uN p’Tit véLo dAnS La Tête}{}{Grenoble, France}{}{Nonprofit self-repair workshop aiming at teaching bicycle mechanics and promoting bike riding.
    \begin{itemize}
        \item Learned bicycle mechanics by dismantling and repairing bikes for the association
        \item Explained to members of the association how to repair their bikes
        \item Took part in meetings and helped organize events as a member of the board from Sep. 2018 to Feb. 2020
    \end{itemize}
}
%\cventry{2013 -- 2014\\(7 months)}{Tutor for homework assistance}{Trait d'Union program}{Villeurbanne, France}{}{Homework assistance program for students from high schools in disadvantaged areas (2 hours/week).
    %    \begin{itemize}
    %        \item Supervised high school students while they were doing their homework (two hours a week)
    %        \item Met people from varied social and cultural background
    %    \end{itemize}
%}

\section{Skills}
\subsection{Languages}
\cvdoubleitem[0.4em]{English}{fluent}{Italian}{good comprehension (B2)}
\cvdoubleitem[0.4em]{French}{native speaker}{Swedish}{currently learning (B1)}

\subsection{Computer}
\cvitem[0.4em]{Programming}{Python, Git, Matlab, C++}
\cvitem[0.4em]{Operating systems}{Linux, Windows, MacOS}
\cvitem[0.4em]{Text processing}{\LaTeX, LibreOffice}

\section{Interests}
\cvitem[0.4em]{Bicycle}{My main mean of transportation since 2017, volunteer mechanics and board member in Do-It-Yourself bicycle workshops.}
\cvitem[0.4em]{Programming}{\colorhref{https://github.com/j4321/}{Open-source software} development with Python, answering questions on \colorhref{https://stackoverflow.com/users/6415268/j-4321}{StackOverflow}.}
\cvitem[0.4em]{Reading}{Novels, mostly mysteries, in English (Michael Connelly, Peter Robinson) and in French (Fred Vargas).}


\end{document}


